A Triple Origin for Twin Blue Stragglers in Close Binaries

### 2019-04-08 response_to_referee3.txt

>> ** I now am more confused on this point. First, both point 5 in the
>> ** Discussion and the abstract say: Consequently, the dominant
>> ** accretor is enriched more effectively by the accreted material,
>> ** and one of the BSs will be more enriched by either CNO-processed
>> ** or s-process elements, depending on whether the donor started to
>> ** overflow its Roche lobe along the red giant or asymptotic giant
>> ** branch, respectively.

>> This would seem to indicate that an AGB star can be the donor? I
>> have a feeling that I am missing something.

>> Second, it is a bit strange that this significant physical point -
>> that this scenario only works for giant donors - is made in a
>> figure caption, without explanation.

We do not think that there is reason for confusion. we wrote: "...,
  but if the donor is an AGB star the enrichment will be mostly in
  s-process elements." For BSS 7782 we exclude this possibility, but
  for other twin blue stragglers we cannot disprove that the donor
  could be an AGB star. In those cases the enrichment of the blue
  stragglers will be different.  But since we do not discuss this any
  further in the paper, we have removed the "s-processed
  element" remark.

@@

>> Other things:

>> >> SPZ/NL: Our prime objective is to demonstrate that this scenario
>>    works. We do not really desire to cover parameter space or indicate
>>    in which part of parameter space this scenario works. This may be
>>    very interesting, but for a future paper.

>> ** I agree with this strategy. I would suggest that it is worth saying this in the paper.

Ok. At the end of the introduction, we added a remark to this extent.
